\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-08-29 methodology.tex
refactoring

To solve this problem, and allow \psharp to be used for testing legacy distributed systems, we decided to take a different approach. Our approach of testing existing distributed systems using \psharp requires three key steps:

@@

\PDComment{Step 1 and 3 are related and thus could combine, also in the following subsections I present 1 and 3 together as the process of ``modeling of environment''}

@@

In the following subsections, we will use the Azure Storage vNext case study as a running example of how to model a typical distributed system using \psharp. In principle, this modeling methodology is not specific to \psharp but can be used in combination with any systematic testing tool. We decided to use \psharp as it is a mature tool that provides a lot of modeling power via its \csharp language extensions and has an embedded systematic concurrency testing engine inside its runtime.

@@

\subsection{Handling intra-machine concurrency}
\label{sec:method:async}

Async/Await

custom schedulers, etc

\subsection{Other}
\label{sec:method:other}

Logs/traces -> user can extend them?

\PDComment{mention dependency injection pattern?}

>>>>

To solve this problem, and allow \psharp to be used for testing legacy distributed systems, we decided to take a different approach. Our approach of testing existing distributed systems using \psharp requires the developer to perform three key modeling tasks:

@@

In the remaining of this section, we will use the Azure Storage vNext case study as a running example of how to model a typical distributed system using \psharp. In principle, this modeling methodology is not specific to \psharp but can be used in combination with any systematic testing tool. We decided to use \psharp as it is a mature tool that provides a lot of modeling power via its \csharp language extensions and has an embedded systematic concurrency testing engine inside its runtime.

In Section~\ref{sec:psharp} we will present more specifics of how the \psharp bug-finding runtime works and extensions that we did since the original work~\cite{deligiannis2015psharp} to be able to use \psharp to systematically test production code.

@@

@@
